### 2019-07-25 thesis.tex
*** empty log message ***

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by very specific conditions
that are unique to each experiment. This specificity makes the analysis in the
experimental context counter productive. A more broad approach is to compare our
theoretical results with plasma phenomena that are independent of imposed laboratory
conditions: astrophysical plasmas.

>>>>

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by very specific conditions
that are unique to each experiment. This specificity makes the analysis in the
experimental context counter productive. A more broad approach was then to compare
our theoretical results with phenomena observed in a naturally occurring space
plasma, that is also accessible to direct measurements. In that sense, the solar
plasma was the logical choice.

It is well known that the plasma in our solar system is considered as a natural
laboratory for the study of space plasma. The wide variety of plasma phenomena
accessible to direct, in situ measurements and highly resolved remote sensing,
might be scaled to other astrophysical environments. Besides that, theoretical
models developed to explain phenomena observed in the solar system plasma might
be extrapolated to describe plasma process occurring in more extreme astrophysical
systems.

% Astrophysical plasmas are observed in a vast range of densities, temperatures,
% magnetic fields, and scale lengths\footnote{The description of such an extensive
%   list is out of the scope of this text. On that matter, Ref.~\cite{peratt2014}
%   offers a quite complete exposure of space plasma, and space plasma phenomena
%   occurring in all cosmic scales.}.

% \footnote{In the literature, the term ``astrophysical plasma'' is sometimes
%   used to refer to the plasma observed outside the solar system, while ``space
%   plasma'' is used to account for the plasma in our interplanetary space. In this
%   text, however, both terms are being used as synonyms.}

% With some exotic exceptions, like the super
% dense and degenerate plasma of white dwarfs (which is beyond the applicability
% of our theory), the solar system hosts a large variety of plasma whose properties

accessible
to both in situ measurements and highly resolved remote sensing.
